What We Eval in the Shadows

### 2021-04-12 analysis/environments.Rmd
Add environment classification for new

```{r}
caller_envs <- env_calls %>% filter(!is.na(hierarchy), is.na(specific_env))
nb_caller_env_sites <- caller_envs %>% pull(src_ref) %>% n_distinct()

@@

@@

```{r}
high_level_new <- env_calls %>% filter(!is.na(new_env)) %>% 
  mutate(category = case_when(
    !is.na(hierarchy) ~ "function",
    specific_env == "global" ~ "global",
    specific_env == "empty" ~ "empty",
    str_detect(specific_env, fixed("loop")) ~ "other",
    !is.na(specific_env) ~ "package"
  ))

@@

nrows <- 5
r_vec("new env category name", nrows, high_level_new_sites$category)
r_vec("new env category sites", nrows, high_level_new_sites$n)
r_vec("new env category site percent", nrows, high_level_new_sites$pc)
```

## The final high-lelve classification

>>>>

```{r}
caller_envs <- env_calls %>% filter(!is.na(hierarchy), is.na(specific_env) || specific_env == "_callee", is.na(new_env))

loop_envs <- env_calls %>% filter(is.na(new_env), str_detect(specific_env, fixed("loop")))

caller_envs <- bind_rows(caller_envs, loop_envs)

nb_caller_env_sites <- caller_envs %>% pull(src_ref) %>% n_distinct()

@@

```{r}
# TODO: high-level per caller frame number...
```

@@

```{r}
high_level_new <- env_calls %>% filter(!is.na(new_env)) %>% 
  mutate(category = case_when(
    !is.na(hierarchy) ~ "function", # Will also include _callee
    specific_env == "global" ~ "global",
    specific_env == "empty" ~ "empty",
    str_detect(specific_env, fixed("loop")) ~ "function", #if it is loop, it means that we found the eval env in the frames,
    !is.na(specific_env) ~ "package"
  ))

@@

nrows <- 4
r_vec("new env category name", nrows, high_level_new_sites$category)
r_vec("new env category sites", nrows, high_level_new_sites$n)
r_vec("new env category site percent", nrows, high_level_new_sites$pc)
```

## The final high-level classification

### 2021-04-12 paper/main.tex
Add environment classification for new

\begin{itemize}
	\item function environments: the frame of the calling function or one of the parent frames (obtained using \c{parent.frame()}, \c{sys.frame()} or with an integer argument for \c{envir} for instance);
	\item list environments: a list, a data frame, a tibble, or \c{NULL} (seen as the empty list), passed to \eval;
	\item the global environment;
	\item package and namespace environments;
	\item the empty environment (created with \c{emptyenv()})
\end{itemize}
We also consider an orthogonal category: environments built with \c{new.env}. They can have as parent an environment of any of the other categories or another environment built with \c{new.env}.

@@

>>>>

\begin{itemize}
	\item function environments: the frame of the calling function or one of the parent frames (obtained using \c{parent.frame()}, \c{sys.frame()} or with an integer argument for \c{envir} for instance);
	\item list environments: a list, a data frame, a tibble, or \c{NULL} (seen as the empty list), passed to \eval;
	\item the global environment;
	\item package and namespace environments;
	\item the empty environment (created with \c{emptyenv()})
\end{itemize}

@@

\begin{table}[h]
    \centering 
    \begin{tabular}{|c|c|c|}
        \hline
        Category & \#sites & \%sites \\
        \hline
        \packageNewEnvCategoryNamea & \packageNewEnvCategorySitesa & \packageNewEnvCategorySitePercenta \\
        \hline
        \packageNewEnvCategoryNameb & \packageNewEnvCategorySitesb &  \packageNewEnvCategorySitePercentb\\
        \hline
        \packageNewEnvCategoryNamec & \packageNewEnvCategorySitesc & \packageNewEnvCategorySitePercentc \\
        \hline
        \packageNewEnvCategoryNamed & \packageNewEnvCategorySitesd & \packageNewEnvCategorySitePercentd \\
        \hline
    \end{tabular}
\caption{Classification of environments wrapped by one of several \c{new}, in number of sites. Some sites can be passed more than one kind of environments. }
\end{table}
